Something something

### 2024-08-28 paper/ms.tex
Insert figures into paper
Add figure captions

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/172175.pdf}
  \caption{\textbf{Test.}}
  \label{fig:fig1}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/392276.pdf}
  \caption{\textbf{When old stars are $\alpha$-enhanced, our subhalo of interest from TNG displays a prominent bimodality.} The upper left panel shows the distribution in the \MgFe{}-\FeH{} plane of the Milky Way, demonstrating a clear bimodality (data selection given in text). The lower left panel shows the 1D histograms of \MgFe{} at fixed \FeH{} values of $-0.5$, $-0.25$, $0$, and $0.25$ (blue, orange, green, and red, respectively). In the Milky Way, the bimodality is strongest at low metallicities while disappearing at high metallicities. The middle column shows the same plots but for our TNG subhalo of interest (392276) and with the fixed \FeH{} values $0.25\,\dex$ lower. No clear bimodality is detected at any metallicity. The right column shows the same subhalo but after increasing the \MgFe{} value of star particles formed before $z=1.5$ linearly with formation time (specifically by incrementing \MgFe{} by $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ if $t_{\textrm{form}} < t_{1.5}$, where $t_{1.5}$ is the age of the universe at $z=1.5$). A clear bimodality is shown in these panels which, unlike in the Milky Way, is present at all metallicities.}
  \label{fig:fig1}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/392276_alpha.pdf}
  \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs in simulation.} The upper panels show \MgFe{} as a function of age for our subhalo in TNG. The colors indicate stellar populations at fixed values of \FeH{}, which are the same as in Figure~\ref{fig:fig1}. A gap in the relation occurs at an age of approximately $10.75\,\Gyr$, which we indicate with a vertical dashed line. The effect of the $\alpha$-enhancement is clear, as it more clearly separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$). The lower panels show on the left the Milky Way and on the center and right the data from TNG but with $10\%$ age errors and $0.01\,\dex$ errors in \MgFe{}. When the simulations are given these errors, we see that the before and after star particles smear such that the two populations significantly overlap in ages. This feature more closely resembles the Milky Way, which displays such populations where the bimodality is strongest -- $\FeH=-0.5$ (blue) and $-0.25$ (orange).}
  \label{fig:alpha}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200.pdf}
  \caption{\textbf{The evolutionary history of our subhalo of interest.} The upper panel shows the SFH of our subhalo. This SFH is generated using the formation times of all star particles in the subhalo at $z=0$. In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha}, which delineates the separation between the high- and low-$\alpha$ sequences. The gap in ages is naturally associated with a gap in the SFH located at the dashed line. The middle panel shows the BH accretion rate as a fraction of the maximum (Eddington) accretion rate across time. At early times the accretion rate is high, but the gap in ages is also coincident with a local spike in the accretion rate. In the lower panel we show the mass assembly of the halo, given as the mass within the radius that encloses $200\times$ the mean density of the universe. In this plot mergers are shown as sudden increases in the halo mass. Mergers at very early times when the halo is signifcantly less massive than its $z=0$ mass are not shown, but one can see that no clear merger is associated with the gap in stellar ages. Two mergers occur later on at $t\sim9$ and $\sim12\,\Gyr$.}
  \label{fig:history}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/mgfe_vice.pdf}
  \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one zone chemical evolution model, described in the text. The upper panel shows the evolution over $2\,\Gyr$ of \MgFe{} while the lower panel shows the negative of its time derivative. Decreasing the star formation timescale $\tau_{\star}=M_{\textrm{gas}/\textrm{SFR}}$ leads to a more rapid decline in \MgFe{}. At its steepest decline ($t\sim0.5\,\Gyr$), an order of magnitude decrease in $\tau_{\star}$ leads to a slope nearly a factor of $2$ larger. At later times ($t>1\,\Gyr$), the models with smaller $\tau_{\star}$ reach their steady-state \MgFe{} value more quickly.}
  \label{fig:vice}
\end{figure}
